A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-13 6_validation.tex
rework beading schemes: remove framework parameters (reviewer 3.7)

\todo{limitations}
}

>>>>

The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
$\alpha_\text{max} = \SI{135}{\degree}$ corresponds to $w^* / \cos \nicefrac12 \alpha_\text{max} = \SI{0.4}{\milli\meter}$ long segments.

\todo{
limitations

mention single bead points here?
}

}
